What do incoming university students believe about open science practices in

### 2021-02-10 analysis/Manuscript.Rmd
removed a half-written sentence

Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice. In other words, students' naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than "business as usual" practices. Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists. Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007]. In relation to open science practices more specifically, a survey of senior French scientists [@schopfelReadyFutureSurvey2016] found that around one in ten were un

It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more of reinforcing "naive" assumptions. In fact, although beyond the scope of this article, it may even be the case that incoming undergraduate students more strongly endorse open science norms than do academics.

<!-- I think it'd be useful here if we were able to point to examples of the anecdotal evidence mentioned above - anyone come across anything (even just on social media?) -->

>>>>

Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice. In other words, students' naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than "business as usual" practices. Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists. Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007]. It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more of reinforcing "naive" assumptions. In fact, although beyond the scope of this article, it may even be the case that incoming undergraduate students more strongly endorse open science norms than do academics.

<!-- I think it'd be useful here if we were able to point to examples of the anecdotal evidence mentioned above - anyone come across anything (even just on social media?) 
Also maybe add more about what we know about academics' endorsement of open science norms.
-->
